---
format:
  html:
    toc: true
    toc-depth: 3
    toc-title: Section
    toc-location: right
    page-layout: full
from: markdown+emoji  
---

```{r}
#| label: cvevents
#| echo: false

cvevents <- function(tbl, when, what, where, details = NULL) {
  result <- ""

  for (i in seq_len(nrow(tbl))) {
    block <- '<div class="cvevent">\n'
    
    # Left column
    block <- paste0(block, '  <div class="cvevent-left">\n')
    block <- paste0(block, '    <strong>', tbl[[what]][i], '</strong><br/>\n')
    block <- paste0(block, '    <em>', tbl[[where]][i], '</em><br/>\n')

    if (!is.null(details)) {
      detail_items <- tbl[[details]][[i]]

      if (length(detail_items) > 0) {
        block <- paste0(block, '    <ul>\n')
        for (item in detail_items) {
          # Auto-link any URLs in item
          item <- gsub("(https?://[^\\s)]+)", "<a href='\\1' target='_blank' rel='noopener noreferrer'>\\1</a>", item, perl = TRUE)
          block <- paste0(block, '      <li>', item, '</li>\n')
        }
        block <- paste0(block, '    </ul>\n')
      }
    }

    block <- paste0(block, '  </div>\n')

    # Right column (date)
    block <- paste0(
      block,
      '  <div class="cvevent-right">',
      tbl[[when]][i],
      '</div>\n'
    )

    block <- paste0(block, '</div>\n\n')
    result <- paste0(result, block)
  }

  knitr::asis_output(result)
}

```

## Current Position

```{r}
#| label: experience
#| output: asis
#| echo: false
tibble::tribble(
    ~role, ~institution, ~dates, ~details, ~tasks,
    "Postdoctoral Researcher", "Department of Psychology, University of Southern Denmark, Denmark", " 01/01/2026 - Present",
    " ", c(    "Dual-sensory loss: audio-visual perception in macular degeneration coupled with loss of auditory functions",
      "Collaborations:
        <ul style='margin-top:0.1em; margin-bottom:0.1em'>
          <li>The Audiology Department (Prof. Tobias Neher)</li>
          <li>The Eriksholm Research Centre (Dr. Dorothea Wendt)</li>
          <li>The Department of Audiology (Dr. Rikke Schnack-Petersen) at Odense University Hospital</li>
          <li>The Department of Ophthalmology (Prof. Jakob Grauslund) at Odense University Hospital</li>
    </ul>",
    "Supervisor: Prof. Søren Krogh Andersen")) |>
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")
```

## Education

```{r }
#| label: education
#| output: asis
#| echo: false
tibble::tribble(
    ~degree, ~institution, ~dates, ~details,
    "Ph.D. in Psychological Sciences", "University of Padova, Italy", "01/10/2021 - 30/09/2024", 
      c("Thesis: Subjective appearance and objective discrimination of shapes in the periphery of the visual field", "https://www.research.unipd.it/handle/11577/3555573",
        "Supervisors: Prof. Marco Bertamini, Prof. Luca Battaglini"),
    "Master Degree in Neuroscience and Neuropsyhcological Rehabilitation", "University of Padova, Italy", "01/10/2017 - 23/05/2020", 
      c("Thesis:  Perceptual learning improves visual functions in albinistic amblyopia", "Supervisor: Prof. Clara Casco"),
    "Bachelor Degree in Sciences and Techniques of Clinical and Health
Psychology", "University of Pisa, Italy", "01/10/2014 - 13/09/2017",NULL
) |>
  cvevents(when = "dates", what = "degree", where = "institution", details = "details")
```

\newpage

## Previous Positions

```{r}
#| label: research_experience
#| output: asis
#| echo: false
tibble::tribble(
  ~degree, ~institution, ~dates, ~details,
  
  "Postdoctoral Researcher",
  "Department of General Psychology, University of Padova, Italy",
  "01/10/2024 - 30/09/2025",
  c(
    "Project: Object ReCognition datA (ORCA)",
    "Collection and analysis of a large EEG dataset",
    "Focus on neural responses to object images across categories and symmetry",
    "Supervisor: Prof. Marco Bertamini"
  ),
  
  "Research Assistant, Visual Perception Lab",
  "Department of General Psychology, University of Padova, Italy",
  "30/01/2021 - 30/09/2021",
  c(
    "Data collection for a behavioural experiment on shape perception in the visual periphery",
    "Focus on the interplay between foveal and peripheral vision",
    "Supervisor: Prof. Marco Bertamini"
  ),
  
  "Research Assistant, NeuroVis.U.S. Lab",
  "Department of General Psychology, University of Padova, Italy",
  "22/03/2018 - 23/05/2020",
  c(
    "Study of the effects of a perceptual learning paradigm in patients with bilateral amblyopia secondary to albinism",
    "Supervisor: Prof. Clara Casco"
  )
) |>
  cvevents(when = "dates", what = "degree", where = "institution", details = "details")

```

\newpage

## Mobility

```{r}
#| label: Abroad 
#| output: asis
#| echo: false
tibble::tribble(
    ~role, ~institution, ~dates, ~details, ~tasks,
  "Visiting Ph.D.",
  "University of Liverpool, Liverpool, UK",
  "16/02/2024 - 03/03/2024",
  "",
  c(
    "EEG data collection, preprocessing, and analysis of symmetry-induced ERPs",
    "Supervisor: Prof. Alexis Makin"
  ),
  
  "Visiting Ph.D.",
  "École polytechnique fédérale de Lausanne (EPFL), Lausanne, Switzerland",
  "01/03/2023 - 01/06/2023",
  "",
  c(
    "Data collection for behavioural experiments on the dissociation between detection and discrimination of peripheral elements",
    "Comparison between uniform and non-uniform textures",
    "Supervisor: Prof. Michael Herzog")
    ) |>
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")
```

\newpage

## Events

```{r}
#| label: conferences
#| output: asis
#| echo: false

cat("### Conferences\n\n")

tibble::tribble(
  ~year, ~event, ~location,
  
  "2025",
  "European Conference of Visual Perception (ECVP), Mainz, Germany",
  "Poster: Sustained Posterior Negativity (SPN) in response to natural, uncontrolled symmetrical stimuli",
  
  "2025",
  "6th International Brain Stimulation Conference, Kobe, Japan",
  "Poster: Combined transcranial alternating current stimulation and perceptual learning for vision improvement in a single-case study of cone dystrophy",
  
  "2024",
  "European Conference of Visual Perception (ECVP), Aberdeen, Scotland",
  "Talk: The CRIP effect: patterns in central vision interfere with perception of patterns in the periphery",
  
  "2024",
  "Cognitive Science Arena, Brixen, Italy",
  "Talk: The centre shapes the periphery: the importance of elements in the centre in uniformity perception",
  
  "2023",
  "European Conference of Visual Perception (ECVP), Paphos, Cyprus",
  "Poster: Is peripheral object discrimination relying on visual imagery?",
  
  "2023",
  "Cognitive Science Arena, Brixen, Italy",
  "Talk: The Honeycomb Illusion is not an illusion",
  
  "2023",
  "The Science of Consciousness (TSC), Taormina, Italy",
  "Talk: The Honeycomb Illusion is not an illusion",
  
  "2022",
  "European Conference of Visual Perception (ECVP), Nijmegen, The Netherlands",
  "Poster: Foveal feedback in the parvocellular and magnocellular systems: comparing a shape and a non-shape task",
  
  "2022",
  "30° Congresso dell’Associazione Italiana di Psicologia, Padova, Italy",
  "Talk: Foveal retinotopic cortex in peripheral non-shape discrimination tasks: comparing magnocellular and parvocellular systems"
) |>
  cvevents(
    when = "year",
    what = "event",
    where = "location"
  )

```

\newpage

## Publications

<ul>

<li>Contemori, G., Musa, M., Demirkapi, D., Passaggi, M., <strong>Oletto</strong>, C. M., Battaglini, L., & Bertamini, M. (2026). Sustained posterior negativity (SPN) elicited by brief (20 ms) symmetrical stimuli. <em>Frontiers in Psychology, 16</em>. <https://doi.org/10.3389/fpsyg.2025.1657531></li>

<li>Contemori, G., Musa, M., <strong>Oletto</strong>, C. M., Vicentin, S., Battaglini, L., Cona, G., & Bertamini, M. (2025). Metacontrast masking of symmetric stimuli. <em>PLOS ONE, 20</em>(8), e0330019. <https://doi.org/10.1371/journal.pone.0330019></li>

<li><strong>Oletto</strong>, C. M., Contemori, G., Yavuz, E. D., Battaglini, L., Herzog, M., & Bertamini, M. (2025). The CRIP effect: How a pattern in central vision interferes with perception of a pattern in the periphery. <em>Journal of Vision, 25</em>(2), 10. <https://doi.org/10.1167/jov.25.2.10></li>

<li>Bertamini, M., <strong>Oletto</strong>, C. M., & Contemori, G. (2024). The role of uniform textures in making texture elements visible in the visual periphery. <em>Open Mind, 8</em>, 462–482. <https://doi.org/10.1162/opmi_a_00136></li>

<li>Contemori, G., <strong>Oletto</strong>, C. M., Battaglini, L., & Bertamini, M. (2024). On the relationship between foveal mask interference and mental imagery in peripheral object recognition. <em>Proceedings of the Royal Society B: Biological Sciences, 291</em>(2018), 20232867. <https://doi.org/10.1098/rspb.2023.2867></li>

<li>Contemori, G., <strong>Oletto</strong>, C. M., Battaglini, L., Motterle, E., & Bertamini, M. (2023). Foveal feedback in perceptual processing: Contamination of neural representations and task difficulty effects. <em>PLOS ONE, 18</em>(10), e0291275. <https://doi.org/10.1371/journal.pone.0291275></li>

<li><strong>Oletto</strong>, C. M., Contemori, G., Bertamini, M., & Battaglini, L. (2022). The role of foveal cortex in discriminating peripheral stimuli: The sketchpad hypothesis. <em>NeuroSci, 4</em>(1), 9–17. <https://doi.org/10.3390/neurosci4010002></li>

<li>Contemori, G., <strong>Oletto</strong>, C. M., Cessa, R., Marini, E., Ronconi, L., Battaglini, L., & Bertamini, M. (2022). Investigating the role of the foveal cortex in peripheral object discrimination. <em>Scientific Reports, 12</em>, 19952. <https://doi.org/10.1038/s41598-022-23720-w></li>

<li>Battaglini, L., <strong>Oletto</strong>, C. M., Contemori, G., Barollo, M., Ciavarelli, A., & Casco, C. (2021). Perceptual learning improves visual functions in patients with albinistic bilateral amblyopia: A pilot study. <em>Restorative Neurology and Neuroscience, 39</em>(1), 45–59. <https://doi.org/10.3233/RNN-201043></li>

</ul>
