---
format:
  html:
    toc: true
    toc-depth: 3
    toc-title: Section
    toc-location: right
    page-layout: full
from: markdown+emoji  
---

```{r}
#| label: cvevents
#| echo: false

cvevents <- function(tbl, when, what, where, details = NULL) {
  result <- '<style>
    .cvevent { display: flex; justify-content: space-between; margin-bottom: 1em; }
    .cvevent-left { max-width: 75%; }
    .cvevent-right { text-align: right; font-weight: bold; min-width: 15%; }
  </style>\n\n'

  for (i in seq_len(nrow(tbl))) {
    block <- '<div class="cvevent">'
    
    # Left column
    block <- paste0(block, '<div class="cvevent-left">', tbl[[what]][i], '<br/><em>', tbl[[where]][i], '</em>')
    
    if (!is.null(details)) {
      detail_items <- tbl[[details]][[i]]
      if (length(detail_items) > 0) {
        block <- paste0(block, '<ul>')
        for (item in detail_items) {
item <- gsub(
  "(https?://[[:alnum:]/?=&%.:+_-]+)",
  '<a href="\\1" target="_blank" rel="noopener noreferrer">\\1</a>',
  item
)
          block <- paste0(block, '<li>', item, '</li>')
        }
        block <- paste0(block, '</ul>')
      }
    }
    
    block <- paste0(block, '</div>') # close left
    
    # Right column
    block <- paste0(block, '<div class="cvevent-right">', tbl[[when]][i], '</div>')
    
    block <- paste0(block, '</div>\n')
    result <- paste0(result, block)
  }

  knitr::asis_output(result)
}

```

## Current Position

```{r}
#| label: experience
#| output: asis
#| echo: false

tibble::tribble(
  ~role, ~institution, ~dates, ~details,
  "<b>Postdoctoral Researcher</b>", 
  "Department of Psychology, University of Southern Denmark, Denmark", 
  "01/01/2026 - Present",
  "Dual-sensory loss: audio-visual perception in macular degeneration coupled with loss of auditory functions.<br>Supervisor: Prof. Søren Krogh Andersen"
) |> 
cvevents(
  when = "dates", 
  what = "role", 
  where = "institution", 
  details = "details"
)
```

## Education

```{r }
#| label: education
#| output: asis
#| echo: false
tibble::tribble(
    ~degree, ~institution, ~dates, ~details,
    "<b>Ph.D. in Psychological Sciences</b>", "University of Padova, Italy", "01/10/2021 - 30/09/2024", 
      c("Thesis: Subjective appearance and objective discrimination of shapes in the periphery of the visual field", "https://www.research.unipd.it/handle/11577/3555573",
        "Supervisors: Prof. Marco Bertamini, Prof. Luca Battaglini"),
    "<b>Master Degree in Neuroscience and Neuropsyhcological Rehabilitation</b>", "University of Padova, Italy", "01/10/2017 - 23/05/2020", 
      c("Thesis:  Perceptual learning improves visual functions in albinistic amblyopia", "Supervisor: Prof. Clara Casco"),
    "<b>Bachelor Degree in Sciences and Techniques of Clinical and Health
Psychology</b>", "University of Pisa, Italy", "01/10/2014 - 13/09/2017",NULL
) |>
  cvevents(when = "dates", what = "degree", where = "institution", details = "details")
```

## Previous Positions

```{r}
#| label: research_experience
#| output: asis
#| echo: false
tibble::tribble(
  ~degree, ~institution, ~dates, ~details,
  
  "<b>Postdoctoral Researcher</b>",
  "Department of General Psychology, University of Padova, Italy",
  "01/10/2024 - 30/09/2025",
  c(
    "Project: Object ReCognition datA (ORCA)",
    "Collection and analysis of a large EEG dataset",
    "Focus on neural responses to object images across categories and symmetry",
    "Supervisor: Prof. Marco Bertamini"
  ),
  
  "<b>Research Assistant</b>",
  "Visual Perception Lab, Department of General Psychology, University of Padova, Italy",
  "30/01/2021 - 30/09/2021",
  c(
    "Data collection for a behavioural experiment on shape perception in the visual periphery",
    "Focus on the interplay between foveal and peripheral vision",
    "Supervisor: Prof. Marco Bertamini"
  ),
  
  "<b>Research Assistant</b>",
  "NeuroVis.U.S. Lab, Department of General Psychology, University of Padova, Italy",
  "22/03/2018 - 23/05/2020",
  c(
    "Study of the effects of a perceptual learning paradigm in patients with bilateral amblyopia secondary to albinism",
    "Supervisor: Prof. Clara Casco"
  )
) |>
  cvevents(when = "dates", what = "degree", where = "institution", details = "details")

```

## Mobility

```{r}
#| label: Abroad 
#| output: asis
#| echo: false
tibble::tribble(
    ~role, ~institution, ~dates, ~details, ~tasks,
  "<b>Visiting Ph.D.</b>",
  "University of Liverpool, Liverpool, UK",
  "16/02/2024 - 03/03/2024",
  "",
  c(
    "EEG data collection, preprocessing, and analysis of symmetry-induced ERPs",
    "Supervisor: Prof. Alexis Makin"
  ),
  
  "<b>Visiting Ph.D.</b>",
  "École polytechnique fédérale de Lausanne (EPFL), Lausanne, Switzerland",
  "01/03/2023 - 01/06/2023",
  "",
  c(
    "Data collection for behavioural experiments on the dissociation between detection and discrimination of peripheral elements",
    "Comparison between uniform and non-uniform textures",
    "Supervisor: Prof. Michael Herzog")
    ) |>
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")
```

## Events

```{r}
#| label: workshops
#| output: asis
#| echo: false

cat("### Workshops & Invited Talks\n\n")

tibble::tribble(
  ~date, ~event, ~location, ~details,
  
  "24/08/2025",
  "A Practical Introduction to Evidence Accumulation Models in Visual Perception Research, European Conference of Visual Perception (ECVP)",
  "Mainz, Germany",
  "https://mar-cald.github.io/eam-workshop/eam-home.html",
  
  "27/05/2025",
  "Subjective appearance and objective discrimination of shapes in the periphery of the visual field, Max Planck Institute for Biological Cybernetics",
  "Tübingen, Germany",
  "https://www.mph.tuebingen.mpg.de/events/41944/2911",
  
  "09/10/2024",
  "Peripheral Vision: What Are Its Limits and Hidden Strengths? (The CRIP effect: patterns in central vision interfere with perception of patterns in the periphery)",
  "Padova, Italy",
  "https://mediaspace.unipd.it/media/La+mia+riunione/1_keutudso?st=451"
) |>
  cvevents(
    when = "date",
    what = "event",
    where = "location",
    details = "details"
  )
```

```{r}
#| label: conferences
#| output: asis
#| echo: false

cat("### Conferences\n\n")

tibble::tribble(
  ~year, ~what, ~where,
  
  "2025",
  "<b>European Conference of Visual Perception, ECVP, Mainz, Germany</b>",
  "Poster: Sustained Posterior Negativity (SPN) in response to natural, uncontrolled symmetrical stimuli",
  
  "2025",
  "<b>6th International Brain Stimulation Conference, Kobe, Japan</b>",
  "Poster: Combined transcranial alternating current stimulation and perceptual learning for vision improvement in a single-case study of cone dystrophy",
  
  "2024",
  "<b>European Conference of Visual Perception, ECVP, Aberdeen, Scotland</b>",
  "Talk: The CRIP effect: patterns in central vision interfere with perception of patterns in the periphery",
  
  "2024",
  "<b>Cognitive Science Arena, Brixen, Italy</b>",
  "Talk: The centre shapes the periphery: the importance of elements in the centre in uniformity perception",
  
  "2023",
  "<b>European Conference of Visual Perception, ECVP, Paphos, Cyprus</b>",
  "Poster: Is peripheral object discrimination relying on visual imagery?",
  
  "2023",
  "<b>Cognitive Science Arena, Brixen, Italy</b>",
  "Talk: The Honeycomb Illusion is not an illusion",
  
  "2023",
  "<b>The Science of Consciousness, TSC, Taormina, Italy</b>",
  "Talk: The Honeycomb Illusion is not an illusion",
  
  "2022",
  "<b>European Conference of Visual Perception, ECVP, Nijmegen, Netherlands</b>",
  "Poster: Foveal feedback in the parvocellular and magnocellular systems: comparing a shape and a non-shape task",
  
  "2022",
  "<b>30° Congresso dell’Associazione Italiana di Psicologia, Padova, Italy</b>",
  "Talk: Foveal retinotopic cortex in peripheral non-shape discrimination tasks: comparing magno and parvocellular system"
) |>
cvevents(
  when = "year",
  what = "what",
  where = "where"
)
```

```{r}
#| label: summer_school
#| output: asis
#| echo: false

cat("### Summer School\n\n")

tibble::tribble(
  ~date, ~event, ~location,
  
  "01/09/2024 – 13/09/2024",
  "<b>Summer School in Visual Neuroscience – From spikes to awareness</b>",
  "Rauischholzhausen, Marburg, Germany"
) |>
  cvevents(
    when = "date",
    what = "event",
    where = "location"
  )
```

## Teaching and Supervision Experience

```{r}
#| label: teaching
#| output: asis
#| echo: false

cat("### Teaching Experience\n\n")

tibble::tribble(
  ~year, ~role, ~details,
  
  "2025",
  "<b>Lecturer, Università di Padova, Padova, Italy</b>",
  "Course: Transcranial Electrical Stimulation (tES) (20 hours)",
  
  "2024",
  "<b>Teaching Assistant, Università di Padova, Padova, Italy</b>",
  "Course: Cognition and Sensory Perception (15 hours)",
  
  "2024",
  "<b>Lecturer, Università di Padova, Padova, Italy</b>",
  "Course: Transcranial Electrical Stimulation (tES) (20 hours)",
  
  "2023",
  "<b>Teaching Assistant, Università di Padova, Padova, Italy</b>",
  "Course: Basic Concepts of Psychology (10 hours)",
  
  "2022",
  "<b>Teaching Assistant, Università di Padova, Padova, Italy</b>",
  "Course: Basic Concepts of Psychology (10 hours)"
) |>
  cvevents(
    when = "year",
    what = "role",
    where = "details"
  )
```

```{r}
#| label: supervision
#| output: asis
#| echo: false

cat("\n\n### Supervision\n\n")

tibble::tribble(
  ~year, ~what, ~where, ~details,
  
  "2024",
  "Bachelor Thesis, Università di Padova, Padova, Italy (Co-Supervisor)", "The effect of a central pattern on peripheral discrimination at different degrees of uniformity perception.",
  "https://hdl.handle.net/20.500.12608/79557",
  
  "2023",
  "Bachelor Thesis, Università di Padova, Padova, Italy (Co-Supervisor)", "The Honeycomb illusion: Peripheral vision of contours, unlike that of objects, is refractory to predictions, extrapolation and memory effects.",
  "https://hdl.handle.net/20.500.12608/51540",
  
  "2022",
  "Bachelor Thesis, Università di Padova, Padova, Italy (Co-Supervisor)", "Fenomenologia della percezione e illusioni ottiche: il caso dell’Honeycomb illusion.",
  "https://thesis.unipd.it/retrieve/2b8a5a3a-ae09-4afb-af9a-274f2bbeca6f/Cepparrone_Freda_Federica.pdf"
) |>
cvevents(
  when = "year",
  what = "what",
  where = "where",
  details = "details"
)
```

## Publications

<ul>

<li>Contemori, G., Musa, M., Demirkapi, D., Passaggi, M., <strong>Oletto</strong>, C. M., Battaglini, L., & Bertamini, M. (2026). Sustained posterior negativity (SPN) elicited by brief (20 ms) symmetrical stimuli. <em>Frontiers in Psychology, 16</em>. <https://doi.org/10.3389/fpsyg.2025.1657531></li>

<li><strong>Oletto</strong>, C. M., Contemori, G., Cessa, R., Battaglini, L., & Bertamini, M. (2026). Foveal masking impairs orientation discrimination of peripheral low-level stimuli. <em>Heliyon, 12</em>(1), e44279. <https://doi.org/10.1016/j.heliyon.2025.e44279></li>

<li>Contemori, G., Musa, M., <strong>Oletto</strong>, C. M., Vicentin, S., Battaglini, L., Cona, G., & Bertamini, M. (2025). Metacontrast masking of symmetric stimuli. <em>PLOS ONE, 20</em>(8), e0330019. <https://doi.org/10.1371/journal.pone.0330019></li>

<li><strong>Oletto</strong>, C. M., Contemori, G., Yavuz, E. D., Battaglini, L., Herzog, M., & Bertamini, M. (2025). The CRIP effect: How a pattern in central vision interferes with perception of a pattern in the periphery. <em>Journal of Vision, 25</em>(2), 10. <https://doi.org/10.1167/jov.25.2.10></li>

<li>Bertamini, M., <strong>Oletto</strong>, C. M., & Contemori, G. (2024). The role of uniform textures in making texture elements visible in the visual periphery. <em>Open Mind, 8</em>, 462–482. <https://doi.org/10.1162/opmi_a_00136></li>

<li>Contemori, G., <strong>Oletto</strong>, C. M., Battaglini, L., & Bertamini, M. (2024). On the relationship between foveal mask interference and mental imagery in peripheral object recognition. <em>Proceedings of the Royal Society B: Biological Sciences, 291</em>(2018), 20232867. <https://doi.org/10.1098/rspb.2023.2867></li>

<li>Contemori, G., <strong>Oletto</strong>, C. M., Battaglini, L., Motterle, E., & Bertamini, M. (2023). Foveal feedback in perceptual processing: Contamination of neural representations and task difficulty effects. <em>PLOS ONE, 18</em>(10), e0291275. <https://doi.org/10.1371/journal.pone.0291275></li>

<li><strong>Oletto</strong>, C. M., Contemori, G., Bertamini, M., & Battaglini, L. (2022). The role of foveal cortex in discriminating peripheral stimuli: The sketchpad hypothesis. <em>NeuroSci, 4</em>(1), 9–17. <https://doi.org/10.3390/neurosci4010002></li>

<li>Contemori, G., <strong>Oletto</strong>, C. M., Cessa, R., Marini, E., Ronconi, L., Battaglini, L., & Bertamini, M. (2022). Investigating the role of the foveal cortex in peripheral object discrimination. <em>Scientific Reports, 12</em>, 19952. <https://doi.org/10.1038/s41598-022-23720-w></li>

<li>Battaglini, L., <strong>Oletto</strong>, C. M., Contemori, G., Barollo, M., Ciavarelli, A., & Casco, C. (2021). Perceptual learning improves visual functions in patients with albinistic bilateral amblyopia: A pilot study. <em>Restorative Neurology and Neuroscience, 39</em>(1), 45–59. <https://doi.org/10.3233/RNN-201043></li>

</ul>

## Conference Proceedings

<ul>

<li><strong>Oletto</strong>, C. M., Ghiani, A., Battaglini, L., Vallesi, A., Bisiacchi, P., Makin, A., & Bertamini, M. (2025). Sustained posterior negativity (SPN) in response to natural, uncontrolled symmetrical stimuli. <em>Proceedings of the 47th European Conference on Visual Perception (ECVP)</em>, Mainz, Germany. <https://ecvp2025.uni-mainz.de/wp-content/uploads/2025/08/List_of_contributions_ECVP2025-v2.pdf></li>

<li><strong>Oletto</strong>, C. M., Khodami, M. A., Carabba, F., et al. (2025). Combined transcranial alternating current stimulation and perceptual learning for vision improvement in a single-case study of cone dystrophy. <em>Brain Stimulation, 18</em>, 455. <https://doi.org/10.1016/j.brs.2024.12.705></li>

<li><strong>Oletto</strong>, C. M., Contemori, G., Battaglini, L., Herzog, M. H., Bertamini, M. (2024). The CRIP effect: patterns in central vision interfere with perception of patterns in the periphery. <em>Proceedings of the 46th European Conference on Visual Perception (ECVP)</em>, Aberdeen, Scotland. <https://journals.sagepub.com/pb-assets/cmscontent/PEC/ECVP%202024%20Abstracts-1742366759.pdf></li>

<li>Bertamini, M., Contemori, G., Battaglini, L., & <strong>Oletto</strong>, C. M. (2023). The honeycomb illusion: Peripheral vision of contours, unlike that of objects, is refractory to predictions, extrapolation and memory effects. <em>Proceedings of the 45th European Conference on Visual Perception (ECVP)</em>, Paphos, Cyprus. <https://journals.sagepub.com/pb-assets/ecvp23_abstracts_UPD-1702301447867.pdf></li>

<li>Contemori, G., <strong>Oletto</strong>, C. M., Di Dona, G., Ronconi, L., Battaglini, L., & Bertamini, M. (2023). Entrainment of perceptually relevant brain oscillations in visual contour integration: Evidence from tACS and audio-visual entrainment. <em>Proceedings of the 45th European Conference on Visual Perception (ECVP)</em>, Paphos, Cyprus. <https://journals.sagepub.com/pb-assets/ecvp23_abstracts_UPD-1702301447867.pdf></li>

<li><strong>Oletto</strong>, C. M., Contemori, G., Battaglini, L., & Bertamini, M. (2023). Is peripheral object discrimination relying on visual imagery? <em>Proceedings of the 45th European Conference on Visual Perception (ECVP)</em>, Paphos, Cyprus. <https://journals.sagepub.com/pb-assets/ecvp23_abstracts_UPD-1702301447867.pdf></li>

<li>Contemori, G., <strong>Oletto</strong>, C. M., Cessa, R., Battaglini, L., & Bertamini, M. (2022). Foveal feedback and the discrimination of peripheral objects: Timing and role. <em>Proceedings of the 44th European Conference on Visual Perception (ECVP)</em>, Nijmegen, The Netherlands. <https://doi.org/10.1177/03010066221141167></li>

<li><strong>Oletto</strong>, C. M., Contemori, G., Battaglini, L., Cessa, R., & Bertamini, M. (2022). Foveal feedback is specific to the parvocellular system but not to shape related tasks. <em>Proceedings of the 44th European Conference on Visual Perception (ECVP)</em>, Nijmegen, The Netherlands. <https://doi.org/10.1177/03010066221141167></li>

</ul>

## Other

```{r}
#| label: collaborations
#| output: asis
#| echo: false

cat("### Collaborations\n\n")

tibble::tribble(
  ~period, ~organization, ~details,
  
  "24/05/2020 – Present",
  "<b>NeuroVis.U.S. Lab, Università di Padova, Department of General Psychology, Padova, Italy</b>",
  "Study of clinical populations with vision loss (amblyopia, hemianopia) and administration of rehabilitative visual training using perceptual learning and transcranial electrical stimulation (tES)"
) |>
  cvevents(
    when = "period",
    what = "organization",
    where = "details"
  )
```

```{r}
#| label: peer_review
#| output: asis
#| echo: false

cat("### Peer Review Contributions\n\n")

tibble::tribble(
  ~year, ~journal, ~reviews,
  
  "2026",
  "I-Perception",
  "Number of peer reviews: 1",
  
  "2025",
  "British Journal of Psychology",
  "Number of peer reviews: 2",
  
  "2025",
  "PLOS ONE",
  "Number of peer reviews: 1",
  
  "2024",
  "Perception",
  "Number of peer reviews: 4",
  
  "2023",
  "Perception",
  "Number of peer reviews: 2"
) |>
  cvevents(
    when = "year",
    what = "journal",
    where = "reviews"
  )
```

```{r}
#| label: Conferences Organisation
#| output: asis
#| echo: false

cat("### Conferences Organisation\n\n")

tibble::tribble(
  ~period, ~organization, ~where, ~details,
  
  "02/10/2025 – 04/10/2025",
  "<b>Behavioural Neuroscience Conference</b>", "Agropoli, Italy",
  "https://behavioural-neuroscience-conference.weebly.com/bn-2025.html",
  
  "19/06/2024 – 21/06/2024",
  "<b>Behavioural Neuroscience Conference (Launch Edition)</b>", "Rome, Italy",
  "https://behavioural-neuroscience-conference.weebly.com/launch-edition-2024.html"
) |>
  cvevents(
    when = "period",
    what = "organization",
    where = "where",
    details = "details"
  )
```

```{r}
#| label: skills
#| output: asis
#| echo: false

cat("### Skills\n\n")

tibble::tribble(
  ~category, ~details, ~where,
  "Languages", "Italian: Native; English: C1; Japanese: A1", "",
  "Programming & Tools", "Python, Matlab (EEGLab and Psychtoolbox), R", "",
  "EEG Systems", "Biosemi, Starstim, Micromed, LiveAmp", "",
  "tES Devices", "BrainStim, Starstim", ""
) |>
cvevents(
  when = "category",
  what = "details",
  where = "where"
)
```
